Regime transition identification for water utilization in river basin developments

### 2020-10-15 tex/main/manuscript.tex
comment some not important references

Throughout the transition phases, three dimensions of water utilization are various in discipline of changes. 
% 水资源压力
(1) Firstly, while stresses on water resources increases when economic expansion boosting water demands, socio-economic progress can response to resource scarcity by better management or efficiency. Water resources were becoming more scarce in the YRB from P1 to P3 (\textit{SI Appendix} Fig. S3). However, water utilization stresses changes a lot rather than always increasing with, because of expansions of farmland, constructions of reservoir, and the increased water use efficiency were all responses and played roles (Figure~\ref{fig:Causes}). Since the scarcity of water resources is directly perceptible and sensitive for utilization, its stresses on societies is one of the most striking drivers to regime shifts within human-water systems \cite{qinFlexibilityIntensityGlobal2019}.
% 水资源倾向性
(2) Secondly, the non-provisioning part of water demands growths with secondary and tertiary industries developing, leading priority of water utilization continually tilted to the socio-economic part. As original region of Ancient Chinese Civilization, the Yellow River Basin used to be dominated by agricultural but in its way to an energy industry zone now \cite{WillEnergyBases}. As a result, saving water consumption in agriculture and making concessions for industry and energy is widely recognized as solutions for the competing \cite{xiangWillEnergyIndustry2016,bebbWaterRightsTransfers2011}. Anyhow, this changes of priority reflect a truth that growing socio-economic parts are responding to scarcity of water resources and contributing to regime shifts.
% 水资源格局
(3) Last, with tighter socio-economic links and comparative advantages between regions and sectors, the geographic scope of water resource supply and demand allocation is expanding, leading to changing configurations of water utilization. In the Yellow River Basin, the gap of water consumptions between regions and sectors are narrowing, as the result of a carefully designed allocation \cite{wangThirtyYearsYellow2018}. However, the configuration of water utilization is determined on the basis of regional and sectoral economic contexts and developing trajectories\cite{wangThirtyYearsYellow2018}. The changes in water utilization configurations along with regime shifts, therefore, are the outcomes of feedbacks within complex human-water systems.

% 综上所述
By combining the above three dimensions, these changes gradually transformed water utilization regimes in a ``natural phase'' (Figure~\ref{fig:summary}A) to one in local or regional phase (Figure~\ref{fig:summary} B and C), towards a comprehensive. In addition to the YRB, human-water relations in major river basins around the world can be explained by the framework. For examples, Indus River, Mississippi River, and Danube River, whose water utilizations have all gone through a relatively natural regime, rapid developments and integrated management regimes. \cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}. In summary, some similar pattern of water utilization can be revealed by the transition framework with basins development.

\section*{Dilemmas and future directions}
% 对于可持续科学，认识这种稳态的变化很重要
% For sustainability scientists, recognizing that different regimes of water utilization regarding different water utilization regimes has important implications for social development and river basin management.
% 不同的流域位于过渡的不同阶段，面临的问题也存在区别，主要包括资源陷阱和结构陷阱两类。
% At different transition phases, however, basins may face to various development dilemmas in water utilization, leading an unsustainable trajectory. 
% % 资源陷阱和失配，导致崩溃
% Like social-ecological systems and other complex systems, coupled human-water system may collapse under the stresses reached the tipping point or structural mismatches 
% \cite{reyersSocialEcologicalSystemsInsights2018,cummingQuantifyingSocialEcologicalScale2020,wangCOSUSTMs0530Review}. 
% % 转型应对陷阱
% A number of studies have identified transformation as an important way out of these unsustainable trajectories, and different types of transformation are required according to dominating regimes and dilemmas of \cite{scoonesTransformationsSustainabilityCombining2020a,steffenTrajectoriesEarthSystem2018}. 
% % 我们的框架有助于理解和识别
Since our transition framework can identify regime shifts of water utilization, it helps to predict possible dilemmas in development.
% 世界各大流域面临的问题。资源开发早期容易陷入资源陷阱；流域发展后期容易陷入结构陷阱。
According to cases all around the world, big river basins often face resource dilemmas after resources-dependent developments, while highly developed ones need to resolve structural problems more often (\textit{SI Appendix} Fig. S11).
% 黄河流域的发展过程，资源开发P2阶段陷入了资源陷阱（表现形式 xxx）。
After the successive exploitation of agriculture, industry and services (refers from natural phase to a local phase in the framework, Figure~\ref{fig:summary}), it is easy for basins to get into a resource dilemma.
% 后来摆脱了资源陷阱（表现形式 xxx）。
As an example, the YRB proposed a clear transformation towards integrated basin management to get rid of the severe resource dilemma, with several management practices. 
% 一段有关87分水方案的介绍
The most important of these is the “87 Water Allocation Scheme”, which adopts a top-down approach in allocating water resources to all regions and sectors \cite{wangThirtyYearsYellow2018}. Since then, the scheme has been revised and refined, and a comprehensive water resources utilization system has gradually been formed that takes the basin scale into account \cite{wangThirtyYearsYellow2018}. 
These integrated management practices made the utilization of water resources into a regime of unified scheduling since the P3 in the Yellow River Basin, to escape from the resource dilemma. 
% 资源困局可能普遍存在
Accelerated development has been followed by severe water scarcity and a series of ecological problems, similar dilemmas are pervasive in basins highly dependent on water resources, where in need of moving towards integrated governance as well 
\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011,unep-dhiTransboundaryRiverBasins2016}.
% 通过协同治理来摆脱困局也普遍存在

>>>>

Throughout the transition phases, three dimensions of water utilization are various in discipline of changes. 
% 水资源压力
(1) Firstly, while stresses on water resources increases when economic expansion boosting water demands, socio-economic progress can response to resource scarcity by better management or efficiency. Water resources were becoming more scarce in the YRB from P1 to P3 (\textit{SI Appendix} Fig. S3). However, water utilization stresses changes a lot rather than always increasing with, because of expansions of farmland, constructions of reservoir, and the increased water use efficiency were all responses and played roles (Figure~\ref{fig:Causes}). Since the scarcity of water resources is directly perceptible and sensitive for utilization, its stresses on societies is one of the most striking drivers to regime shifts within human-water systems \cite{qinFlexibilityIntensityGlobal2019}.
% 水资源倾向性
(2) Secondly, the non-provisioning part of water demands growths with secondary and tertiary industries developing, leading priority of water utilization continually tilted to the socio-economic part. As original region of Ancient Chinese Civilization, the Yellow River Basin used to be dominated by agricultural but in its way to an energy industry zone now \cite{WillEnergyBases}. 
As a result, saving water consumption in agriculture and making concessions for industry and energy is widely recognized as solutions for the competing \cite{xiangWillEnergyIndustry2016,bebbWaterRightsTransfers2011}. Anyhow, this changes of priority reflect a truth that growing socio-economic parts are responding to scarcity of water resources and contributing to regime shifts.
% 水资源格局
(3) Last, with tighter socio-economic links and comparative advantages between regions and sectors, the geographic scope of water resource supply and demand allocation is expanding, leading to changing configurations of water utilization. In the Yellow River Basin, the gap of water consumptions between regions and sectors are narrowing, as the result of a carefully designed allocation
% \cite{wangThirtyYearsYellow2018}. 
However, the configuration of water utilization is determined on the basis of regional and sectoral economic contexts and developing trajectories 
%\cite{wangThirtyYearsYellow2018}. 
The changes in water utilization configurations along with regime shifts, therefore, are the outcomes of feedbacks within complex human-water systems.

% 综上所述
By combining the above three dimensions, these changes gradually transformed water utilization regimes in a ``natural phase'' (Figure~\ref{fig:summary}A) to one in local or regional phase (Figure~\ref{fig:summary}B and Figure~\ref{fig:summary}C), towards a comprehensive. In addition to the YRB, human-water relations in major river basins around the world can be explained by the framework. 
For examples, Indus River, Mississippi River, and Danube River, whose water utilizations have all gone through a relatively natural regime, rapid developments and integrated management regimes. 
%\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011}. 
In summary, some similar pattern of water utilization can be revealed by the transition framework with basins development.

\section*{Dilemmas and future directions}
% 对于可持续科学，认识这种稳态的变化很重要
% For sustainability scientists, recognizing that different regimes of water utilization regarding different water utilization regimes has important implications for social development and river basin management.
% 不同的流域位于过渡的不同阶段，面临的问题也存在区别，主要包括资源陷阱和结构陷阱两类。
% At different transition phases, however, basins may face to various development dilemmas in water utilization, leading an unsustainable trajectory. 
% % 资源陷阱和失配，导致崩溃
% Like social-ecological systems and other complex systems, coupled human-water system may collapse under the stresses reached the tipping point or structural mismatches 
% \cite{reyersSocialEcologicalSystemsInsights2018,cummingQuantifyingSocialEcologicalScale2020,wangCOSUSTMs0530Review}. 
% % 转型应对陷阱
% A number of studies have identified transformation as an important way out of these unsustainable trajectories, and different types of transformation are required according to dominating regimes and dilemmas of \cite{scoonesTransformationsSustainabilityCombining2020a,steffenTrajectoriesEarthSystem2018}. 
% % 我们的框架有助于理解和识别
Since our transition framework can identify regime shifts of water utilization, it helps to predict possible dilemmas in development.
% 世界各大流域面临的问题。资源开发早期容易陷入资源陷阱；流域发展后期容易陷入结构陷阱。
According to cases all around the world, big river basins often face resource dilemmas after resources-dependent developments, while highly developed ones need to resolve structural problems more often (\textit{SI Appendix} Fig. S11).
% 黄河流域的发展过程，资源开发P2阶段陷入了资源陷阱（表现形式 xxx）。
After the successive exploitation of agriculture, industry and services (refers from natural phase to a local phase in the framework, Figure~\ref{fig:summary}), it is easy for basins to get into a resource dilemma.
% 后来摆脱了资源陷阱（表现形式 xxx）。
As an example, the YRB proposed a clear transformation towards integrated basin management to get rid of the severe resource dilemma, with several management practices. 
% 一段有关87分水方案的介绍
The most important of these is the “87 Water Allocation Scheme”, which adopts a top-down approach in allocating water resources to all regions and sectors 
%\cite{wangThirtyYearsYellow2018}. 
Since then, the scheme has been revised and refined, and a comprehensive water resources utilization system has gradually been formed that takes the basin scale into account 
% \cite{wangThirtyYearsYellow2018}. 
These integrated management practices made the utilization of water resources into a regime of unified scheduling since the P3 in the Yellow River Basin, to escape from the resource dilemma. 
% 资源困局可能普遍存在
Accelerated development has been followed by severe water scarcity and a series of ecological problems, similar dilemmas are pervasive in basins highly dependent on water resources, where in need of moving towards integrated governance as well 
\cite{bestAnthropogenicStressesWorld2019,cummingResilienceBigRiver2011,unep-dhiTransboundaryRiverBasins2016}.
% 通过协同治理来摆脱困局也普遍存在
